Changes From Preregistration

### 2023-03-02 manuscript.RmD
- updated abstract

---
title             : "Likes or Dislikes, Gratifications or Concerns? Analyzing Popularity Cues and Privacy Calculus when Communicating Online"
shorttitle        : "Popularity cues & privacy calculus"
abstract: |
    According to privacy calculus, both privacy concerns and expected gratifications explain why people communicate online. So far, most findings were based on self-reports or short-term experiments, and it is still largely unknown how popularity cues such as like and dislike buttons affect privacy calculus. To answer these questions, a preregistered one-week field experiment was conducted. Participants were randomly distributed to three different websites, on which they discussed a current political topic. The websites featured either (a) like buttons, (b) like and dislike buttons, or (c) no like or dislike buttons, and were otherwise identical. The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants. Although the originally preregistered model was largely rejected, the results showed that a considerable share of actual communication could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy. The impact of the popularity cues on privacy calculus and communication was negligible.
keywords          : "privacy calculus, communication, popularity cues, field experiment, structural equation modeling, preregistration"
bibliography      : 
  - [bibliography/r-references.bib]
  - [bibliography/references.bib]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : yes
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
draft             : no
documentclass     : "apa6"
classoption       : "man"
# to compile as pdf
# (a) move file "_site.yml" to folder "archive"
# (b) uncomment the following lines
output            : papaja::apa6_pdf
header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
  - \note{\clearpage}
# output            : papaja::apa6_docx
# output:
#   html_document:
#     toc: TRUE
#     toc_float:
#       collapsed: FALSE
#     toc_depth: 2
---

>>>>

---
title             : "Do Likes Buttons Increase Self-Disclosure? Analyzing how Online Communication is Affected by Popularity Cues Using the Privacy Calculus Model"
shorttitle        : "Popularity cues & privacy calculus"
abstract: |
    How do like and dislike buttons affect online communication? According to the privacy calculus model, online self-disclosure is determined by privacy concerns and expected benefits. It seems possible that like and dislike buttons affect self-disclosure, for example because they increase expected benefits or privacy concerns. To find out, we conducted a preregistered one-week field experiment. Participants were randomly distributed to three different websites, on which they discussed a current political topic. The websites featured either (a) like buttons, (b) like and dislike buttons, or (c) no like or dislike buttons. The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants. The results showed that the mere existence of a like and dislike button did not affect online communication. However, self-disclosure could be predicted successfully using the privacy calculus variables.
keywords          : "privacy calculus, communication, popularity cues, field experiment, structural equation modeling, preregistration"
bibliography      : 
  - [bibliography/r-references.bib]
  - [bibliography/references.bib]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : yes
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
draft             : no
documentclass     : "apa6"
classoption       : "man"
# to compile as pdf
# (a) move file "_site.yml" to folder "archive"
# (b) uncomment the following lines
output            : papaja::apa6_pdf
header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
  - \note{\clearpage}
# output            : papaja::apa6_docx
# output:
#   html_document:
#     toc: TRUE
#     toc_float:
#       collapsed: FALSE
#     toc_depth: 2
---
